### 2023-09-02 sections/2-methods.tex
changes after Sat AM call. Table headers TBD.

\begin{algorithm} % enter the algorithm environment
\caption{ClusterPartition(\emph{C})} % give the algorithm a caption
\label{alg:partition} % and a label for \ref{} commands later in the document
\begin{algorithmic}[1] % enter the algorithmic environment
    \STATE $m \Leftarrow \lfloor \sqrt{|C|} \rfloor$
    \STATE $seeds \Leftarrow m$ random points from $C.points$
    \STATE $c \Leftarrow$ geometric median of $seeds$
    \STATE $l \Leftarrow \argmax d(c,x) \ \forall \ x \in C.points$
    \STATE $r \Leftarrow \argmax d(l,x) \ \forall \ x \in C.points$
    \STATE $left \Leftarrow \{x | x \in C.points \land d(l,x) \le d(r,x)\}$
    \STATE $right \Leftarrow \{x | x \in C.points \land d(r,x) < d(l,x)\}$
    \IF{$|left| > 1$}
        \STATE ClusterPartition($left$)
    \ENDIF
    \IF{$|right| > 1$}
        \STATE ClusterPartition($right$)
    \ENDIF
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=2.5in]{images/geometry/geometry.pdf}
    \caption{Scaling Behavior of Radii in a Two-Dimensional Uniform-Density Disk. $R$ 
    denotes the radius of the root cluster $C$, and $o$ denotes its center. The right 
    triangle formed by $o$, $o'$, and $y+$ in $C'$ shows that $R \leq R'$, where $R'$ is the radius of $C'$.
    Hence, the radius of a child cluster can be larger than its parent. $C''$ 
    illustrates that after we have consumed all $d$ axes, the radius of a child cluster
    is bounded above by $\frac{R}{\sqrt{2}}$.}
    \label{fig:methods:scaling_behavior}
\end{figure}

@@

\begin{algorithm} 
    \caption{$\rho$-NN(\emph{clusters, query, r})} 
    \label{alg:rnn} 
    \begin{algorithmic}[2]
        \REQUIRE $r \geq 0$
        \REQUIRE $clusters \neq \emptyset$
        \STATE $results \Leftarrow \emptyset$
        \IF{$clusters.left \land clusters.left \cap B_X(query, r) \neq \emptyset$}
            \IF{$clusters.left.\delta$ $\leq$ $r$ + $clusters.left.radius$}
                \STATE $\rho$-NN($clusters.left, query, r$)
            \ENDIF
        \ENDIF
        \IF{$clusters.right \land clusters.right \cap B_X(query, r) \neq \emptyset$}
            \IF{$clusters.right.\delta$ $\leq$ $r$ + $clusters.right.radius$} 
                \STATE $\rho$-NN($clusters.right, query, r$)
            \ENDIF
        \ENDIF
        \IF{$\neg$$clusters.left$ $\land \neg$$clusters.right$}
            \FOR{$p \in clusters.points$}
                \IF{$p.\delta \leq r$}
                    \STATE $results.push((p, r))$
                \ENDIF
            \ENDFOR
        \ENDIF
        \STATE Return $results$
    \end{algorithmic}
    \end{algorithm}

The asymptotic complexity of $\rho$-nearest neighbors is the same as in ~\cite{ishaq2019clustered}.

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Repeated$\rho$-NN(\emph{root, query, k})} % give the algorithm a caption
    \label{alg:knn-by-rnn} % and a label for \ref{} commands later in the document
    \begin{algorithmic}[4] % enter the algorithmic environment
        \STATE $H \Leftarrow$ $\emptyset$
        \STATE $m \Leftarrow$ $\frac{root.radius}{|root|}$
        \WHILE {$|H| = 0$}
            \STATE $H.push(\rho$-NN$(root, query, m)$)
            \STATE $m \Leftarrow 2m$
        \ENDWHILE
        \WHILE {$|H| < k$}
            \STATE $Q \Leftarrow \{ C: \exists p \in H \land p \in C \}$
            \STATE $\mu \Leftarrow |Q| \sum_{C \in Q} \frac{1}{C.lfd} $
            \STATE $m \Leftarrow \argmin \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right)$
            \STATE $H.push(\rho$-NN$(root, query, m)$)
        \ENDWHILE
        \STATE $H.sort()$
        \STATE Return $H[0], H[1], \cdots H[k-1]$
    \end{algorithmic}
    \end{algorithm}

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Sieve(\emph{tree, query, k})} % give the algorithm a caption
    \label{alg:sieve} % and a label for \ref{} commands later in the document
    \begin{algorithmic}[6] % enter the algorithmic environment
        \REQUIRE $tree$, $query$, $k$
        \STATE $Q \Leftarrow$ [$tree.root$]
        \WHILE{$|Q| > k$}
            \STATE $i \Leftarrow QuicksortPartition(Q, k, 0, |Q| - 1)$
            \STATE $\tau \Leftarrow Q[i].\delta_{max}$
            \FOR {$q \in Q$}
                \IF {$q.\delta_{min} > \tau$}
                    \STATE $Q.pop(q)$
                \ENDIF
            \ENDFOR
            \FOR {$q \in Q$}
                \IF {$q.isLeaf \lor |q| \leq k$}
                    \STATE $Q.push(q.points)$
                \ELSE
                    \STATE $[l, r] \Leftarrow q.children$
                    \STATE $Q.push([l, r])$   
                \ENDIF
                \STATE $Q.pop(q)$
            \ENDFOR 
        \ENDWHILE
        \STATE Return $Q$
    \end{algorithmic}
    \end{algorithm}

@@

\begin{algorithm} 
\caption{GreedySearch(\emph{root, query, k})} 
\label{alg:greedy_search} 
\begin{algorithmic}[3]
    \STATE $Q \Leftarrow$ priority queue
    \STATE $Q.push(root)$
    \STATE $H \Leftarrow$ priority queue
    \WHILE{$|H| < k \lor H.pop.\delta > Q.pop.\delta_{min}$}
        \WHILE{$\neg Q.pop.isLeaf$}
            \STATE $[l, r] \Leftarrow Q.pop().children$
            \STATE $Q.push([l, r])$
        \ENDWHILE
        \STATE $leaf \Leftarrow Q.pop()$
        \STATE $H.push(leaf)$
        \WHILE{$|H| > k$}
            \STATE $H.pop()$
        \ENDWHILE
    \ENDWHILE
    \STATE Return $H$
\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm} % enter the algorithm environment
\caption{ClusterPartition(\emph{C})} % give the algorithm a caption
\label{alg:partition} % and a label for \ref{} commands later in the document
\begin{algorithmic} % enter the algorithmic environment
    \STATE $m \Leftarrow \lfloor \sqrt{|C|} \rfloor$
    \STATE $seeds \Leftarrow m$ random points from $C.points$
    \STATE $c \Leftarrow$ geometric median of $seeds$
    \STATE $l \Leftarrow \argmax d(c,x) \ \forall \ x \in C.points$
    \STATE $r \Leftarrow \argmax d(l,x) \ \forall \ x \in C.points$
    \STATE $left \Leftarrow \{x | x \in C.points \land d(l,x) \le d(r,x)\}$
    \STATE $right \Leftarrow \{x | x \in C.points \land d(r,x) < d(l,x)\}$
    \IF{$|left| > 1$}
        \STATE ClusterPartition($left$)
    \ENDIF
    \IF{$|right| > 1$}
        \STATE ClusterPartition($right$)
    \ENDIF
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{images/geometry/geometry.pdf}
    \caption{Scaling Behavior of Radii in a Two-Dimensional Uniform-Density Disk. $R$ 
    denotes the radius of the root cluster $C$, and $o$ denotes its center. The right 
    triangle formed by $o$, $o'$, and $y+$ in $C'$ shows that $R \leq R'$, where $R'$ is the radius of $C'$.
    Hence, the radius of a child cluster can be larger than its parent. $C''$ 
    illustrates that after we have consumed all $d$ axes, the radius of a child cluster
    is bounded above by $\frac{R}{\sqrt{2}}$.}
    \label{fig:methods:scaling_behavior}
\end{figure}

@@

\begin{algorithm} 
    \caption{$\rho$-NN(\emph{clusters, query, r})} 
    \label{alg:rnn} 
    \begin{algorithmic}
        \REQUIRE $r \geq 0$
        \REQUIRE $clusters \neq \emptyset$
        \STATE $results \Leftarrow \emptyset$
        \IF{$clusters.left \land clusters.left \cap B_X(query, r) \neq \emptyset$}
            \IF{$clusters.left.\delta$ $\leq$ $r$ + $clusters.left.radius$}
                \STATE $\rho$-NN($clusters.left, query, r$)
            \ENDIF
        \ENDIF
        \IF{$clusters.right \land clusters.right \cap B_X(query, r) \neq \emptyset$}
            \IF{$clusters.right.\delta$ $\leq$ $r$ + $clusters.right.radius$} 
                \STATE $\rho$-NN($clusters.right, query, r$)
            \ENDIF
        \ENDIF
        \IF{$\neg$$clusters.left$ $\land \neg$$clusters.right$}
            \FOR{$p \in clusters.points$}
                \IF{$p.\delta \leq r$}
                    \STATE $results.push((p, r))$
                \ENDIF
            \ENDFOR
        \ENDIF
        \STATE Return $results$
    \end{algorithmic}
    \end{algorithm}

The asymptotic complexity of $\rho$-nearest neighbors is the same as in ~\cite{ishaq2019clustered}, namely:

\begin{gather}
    \mathcal{O}\Bigg(
    \underbrace{\log_2 \mathcal{N}_{\hat{r_c}}(D)}_{\textrm{metric entropy}} +
    \overbrace{\left|B_D(q,r)\right|}^{\textrm{output size}}
    \underbrace{\left(\frac{r+2\hat{r_c}}{r}\right)^d}_{\textrm{scaling factor}}
     \Bigg)
     \label{hierarchical-complexity}
\end{gather}

where $\hat{r_c}$ is the \textit{mean} cluster radius of leaf clusters, $\mathcal{N}_{\hat{r_c}}(D)$ is the metric entropy at that radius, $B_D(q,r)$ is a ball of data points around the query $q$ at search radius $r$, and $d$ is the factal dimension around the query in a region of radius $r$.

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Repeated$\rho$-NN(\emph{root, query, k})} % give the algorithm a caption
    \label{alg:knn-by-rnn} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \STATE $H \Leftarrow$ $\emptyset$
        \STATE $m \Leftarrow$ $\frac{root.radius}{|root|}$
        \WHILE {$|H| = 0$}
            \STATE $H.push(\rho$-NN$(root, query, m)$)
            \STATE $m \Leftarrow 2m$
        \ENDWHILE
        \WHILE {$|H| < k$}
            \STATE $Q \Leftarrow \{ C: \exists p \in H \land p \in C \}$
            \STATE $\mu \Leftarrow |Q| \sum_{C \in Q} \frac{1}{C.lfd} $
            \STATE $m \Leftarrow \argmin \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right)$
            \STATE $H.push(\rho$-NN$(root, query, m)$)
        \ENDWHILE
        \STATE $H.sort()$
        \STATE Return $H[0], H[1], \cdots H[k-1]$
    \end{algorithmic}
    \end{algorithm}

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Sieve(\emph{tree, query, k})} % give the algorithm a caption
    \label{alg:sieve} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \REQUIRE $tree$, $query$, $k$
        \STATE $Q \Leftarrow$ [$tree.root$]
        \WHILE{$|Q| > k$}
            \STATE $i \Leftarrow QuicksortPartition(Q, k, 0, |Q| - 1)$
            \STATE $\tau \Leftarrow Q[i].\delta_{max}$
            \FOR {$q \in Q$}
                \IF {$q.\delta_{min} > \tau$}
                    \STATE $Q.pop(q)$
                \ENDIF
            \ENDFOR
            \FOR {$q \in Q$}
                \IF {$q.isLeaf \lor |q| \leq k$}
                    \STATE $Q.push(q.points)$
                \ELSE
                    \STATE $[l, r] \Leftarrow q.children$
                    \STATE $Q.push([l, r])$   
                \ENDIF
                \STATE $Q.pop(q)$
            \ENDFOR 
        \ENDWHILE
        \STATE Return $Q$
    \end{algorithmic}
    \end{algorithm}

@@

\begin{algorithm} 
\caption{GreedySearch(\emph{root, query, k})} 
\label{alg:greedy_search} 
\begin{algorithmic}
    \STATE $Q \Leftarrow$ priority queue
    \STATE $Q.push(root)$
    \STATE $H \Leftarrow$ priority queue
    \WHILE{$|H| < k \lor H.pop.\delta > Q.pop.\delta_{min}$}
        \WHILE{$\neg Q.pop.isLeaf$}
            \STATE $[l, r] \Leftarrow Q.pop().children$
            \STATE $Q.push([l, r])$
        \ENDWHILE
        \STATE $leaf \Leftarrow Q.pop()$
        \STATE $H.push(leaf)$
        \WHILE{$|H| > k$}
            \STATE $H.pop()$
        \ENDWHILE
    \ENDWHILE
    \STATE Return $H$
\end{algorithmic}
\end{algorithm}

### 2023-09-02 sections/3-datasets.tex
changes after Sat AM call. Table headers TBD.

\subsection{APOGEE-2}
\label{subsec:datasets:apogee-2}
The Sloan Digital Sky Survey (SDSS) [3] Apache Point Observatory Galaxy Evolution
Experiment (APOGEE) [4] contains near-infrared
spectra of approximately 130,000 stellar objects in the Milky
Way galaxy. Each spectral datum describes a star's flux in
Janskys ($1 Jy = 10^{-26} W \dot m^{-2} \dot Hz^{-1}$) at each of 8,575 wavelengths ranging from $\lambda$ = 1.51 µm to 1.70 µm. Thus,
Thus, each datum is a real-valued vector in $\mathbb{R}_{+}^{8575}$.

Astronomers use these near-infrared spectra to achieve a better understanding of our galaxy's history. This dataset 
is often used with Euclidean (L2) distance, cosine distance, and 1d-Wasserstein distance. As illustrated by Figure 1 in Section 2,
this dataset is a good candidate for CAKES because it exhibits low fractal dimension.

\subsection{MaNGA}
\label{subsec:datasets:manga}
SDSS's Mapping Nearby Galaxies at APO (MaNGA) [CITE] contains spectral measurements across the face of each of 
about 10,000 galaxies across 2,700 deg$^2$.

Like APOGEE, MaNGA helps astronomers understand the history of galaxies throughout their entire lifespan. This 
dataset is typically used with Euclidean (L2) distance, cosine distance, and 2d-Wasserstein distance.

TODO: Add details about why this dataset is a good candidate for CAKES.

\subsection{Silva 18S}
\label{subsec:datasets:silva-18s}

Silva 18S contains ribosomal DNA sequences of approximately 2.25 
million genomes with aligned length of 50,000 letters.

These sequences help biologists better understand the evolutionary relationships between organisms. 
This dataset is typically used with Hamming and Levenshtein distances.

TODO: Add details about why this dataset is a good candidate for CAKES.

\dots

@@

We benchmark on a variety of datasets from the ann-benchmarks suite~\cite{Aumller2018ANNBenchmarksAB}, 
which we list below, along with the distance functions with which they are typically used.

\begin{itemize} 
    \item DEEP1B (Cosine): ~1 billion 96-dimensional deep descriptors to 
    \item Fashion-MNIST (Euclidean): 60,000 784-dimensional vector representations of images of clothing items
    \item GIST (Euclidean): 1 million 960-dimensional image descriptors 
    \item GloVe (Cosine): ~1.2 million 25-dimensional vector representations of words
    \item Kosarak (Jaccard): ~75 thousand ~28 thousand-dimensional binary vectors representing user clickstreams
    \item MNIST (Euclidean): 60,000 784-dimensional vector representations of images of handwritten digits
    \item NYTimes (Cosine): 290,000 256-dimensional vector representations of words
    \item SIFT (Euclidean): 1 million 128-dimensional image descriptors
    \item Last.fm (Cosine): ~292, 000 65-dimensional vector representations of songs
\end{itemize}

>>>>

@@

We benchmark on a variety of datasets from the ann-benchmarks suite~\cite{Aumller2018ANNBenchmarksAB}, 
listed below, along with the appropriate distance function.
Table~\ref{table:datasets:summary} summarizes the properties of these datasets.

% \begin{itemize} 
%     \item DEEP1B (Cosine): $\sim$1 billion 96-dimensional deep descriptors to 
%     \item Fashion-MNIST (Euclidean): 60,000 784-dimensional vector representations of images of clothing items
%     \item GIST (Euclidean): 1 million 960-dimensional image descriptors 
%     \item GloVe (Cosine): $\sim$1.2 million 25-dimensional vector representations of words
%     \item Kosarak (Jaccard): $\sim$75 thousand ~28 thousand-dimensional binary vectors representing user clickstreams
%     \item MNIST (Euclidean): 60,000 784-dimensional vector representations of images of handwritten digits
%     \item NYTimes (Cosine): 290,000 256-dimensional vector representations of words
%     \item SIFT (Euclidean): 1 million 128-dimensional image descriptors
%     \item Last.fm (Cosine): $\sim$292, 000 65-dimensional vector representations of songs
% \end{itemize}

\begin{table}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Datasets used in benchmarks.}
    \label{table:datasets:summary}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|l|l|l|}
    \hline
    \textbf{Dataset} & \textbf{Distance}  &\textbf{Cardinality}  & \textbf{Dim.}  \\
    &                &                  &                         \\
    \hline
    nytimes          & cosine              & 290,000            & 256       \\
    \hline
    fashion-mnist    & euclidean              & 60,000             & 784       \\
    \hline 
    gist             & euclidean              & 1,000,000          & 960       \\
    \hline
    glove-25         & cosine              & 1,183,514          & 25        \\
    \hline
    glove-100        & cosine              & 1,183,514          & 100       \\
    \hline
    sift             & euclidean              & 1,000,000          & 128       \\
    \hline
    deep-image       & cosine              & 9,990,000          & 96        \\
    \hline
    mnist            & euclidean              & 60,000             & 784       \\
    \hline
    glove-50         & cosine              & 1,183,514          & 50        \\
    \hline
    lastfm           & cosine              & 292,385            & 65        \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table}

### 2023-09-02 sections/4-results.tex
changes after Sat AM call. Table headers TBD.

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Performance (ROC AUC) of CHAODA vs. other methods on the 18 test datasets.}
    \label{table:results:test-performance}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Dataset} & \textbf{Dist.}  &\textbf{Card.}  & \textbf{Dim.}  & \textbf{k}  & \multicolumn{2}{r}\textbf{faiss-ivf} & \multicolumn{2}{r}\textbf{bruteforce-blas} & \multicolumn{2}{r}\textbf{hnsw(faiss)} & \multicolumn{2}{r}\textbf{CAKES} \\
    &                &                  &                   &               &             Recall & QPS                           & Recall & QPS                           & Recall & QPS                                           & Recall & QPS \\
    \hline
    nytimes          & cos              & 290,000            & 256             & 10         & 0.69 &  1413.35                       & 0.99 & 26.66                            & 0.97 & 92.92                                         & 1.00 & 42 \\
    \hline
    nytimes          & cos              & 290,000            & 256             & 100        & 0.61 &  0.71                          & 0.99 & 10.71                              & 0.00 & 0.00                                          & 1.00 & 42 \\
    \hline
    fashion-mnist    & euc              & 60,000	         & 784            & 10         & 0.54 & 324.79                           & 1.00 & 52.91                                  & 0.94 & 60.89                                                    & 1.00 & 42 \\
    \hline
    fashion-mnist    & euc              & 60,000             & 784            & 100        & 1.00 & 111.47                           & 0.99 & 16.02                                  & 0.99 & 277.80                                                    & 1.00 & 42 \\
    \hline 
    gist             & euc              & 1,000,000          & 960             & 10         & 1.00 & 3.55                           & 1.00 & 2.63                                     & 0.95 & 149.58                                                   & 1.00 & 42 \\
    \hline
    gist             & euc              & 1,000,000          & 960             & 100        & 1.00 & 2.70                           & 0.99 & 0.80                                 & 0.99 & 59.71                                                    & 1.00 & 42 \\
    \hline
    glove-25         & cos              & 1,183,514          & 25             & 10         & 1.00 & 78.78                          & 1.00 & 33.52                              & 1.00 & 552.67                                                  & 1.00 & 42 \\
    \hline
    glove-25         & cos              & 1,183,514          & 25             & 100        & -- & --                                & -- & --                                & -- & --                                                    & 1.00 & 42 \\
    \hline
    glove-100        & cos              & 1,183,514          & 100            & 10         & 1.00 & 21.16                          & 1.00 & 16.52                                & 0.99 & 155.90                                                  & 1.00 & 42 \\
    \hline
    glove-100        & cos              & 1,183,514          & 100            & 100        & 0.99 &  7.52                          & 0.99 & 3.11                                  & 0.99 & 92.58                                                    & 1.00 & 42 \\
    \hline
    sift             & euc              & 1,000,000          & 128            & 10         & 1.00 &  24.52                          & 1.00 & 16.40                               & 1.00 & 275.07                                                    & 1.00 & 42 \\
    \hline
    sift             & euc              & 1,000,000          & 128            & 100        & 1.00 &  23.50                          & 1.00 & 6.51                                  & 0.99 & 179.14                                                    & 1.00 & 42 \\
    \hline
    deep-image       & cos              & 9,990,000	         & 96             & 10          & 0.00 & 0.00                           & 0.00 & 0.00                                 & 0.00 & 0.00                                                     & 1.00 & 42 \\
    \hline
    deep-image       & cos              & 9,990,000	         & 96             & 100         & 0.00 & 0.00                           & 0.00 & 0.00                                & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    mnist            & euc              & 60,000             & 784             & 10          & 0.00 & 0.00                          & 0.00 & 0.00                                 & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    mnist            & euc              & 60,000             & 784             & 100         & 0.00 & 0.00                          & 0.00 & 0.00                                  & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    glove-50         & cos              & 1,183,514          & 50             & 10          & 0.00 & 0.00                           & 0.00 & 0.00                              & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    glove-50         & cos              & 1,183,514          & 50             & 100         & 0.00 & 0.00                           & 0.00 & 0.00                              & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    lastfm           & cos              & 292,385            & 65             & 10          & 0.00 & 0.00                           & 0.00 & 0.00                               & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    lastfm           & cos              & 292,385            & 65             & 100         & 0.00 & 0.00                           & 0.00 & 0.00                             & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}

>>>>

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=10$}
    \label{table:results:ann-10}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|}
    \textbf{Dataset}  & \multicolumn{2}{|c|}\textbf{faiss-ivf} & \multicolumn{2}{|c|}\textbf{bruteforce-blas} & \multicolumn{2}{|c|}\textbf{hnsw(faiss)} & \multicolumn{2}{|c|}\textbf{CAKES} \\
    \cline{2-9}
    &                    Recall & QPS                           & Recall & QPS                           & Recall & QPS                                           & Recall & QPS \\
    \hline
    nytimes                & 0.69 &  1413.35                       & 0.99 & 26.66                            & 0.97 & 92.92                                         & 1.00 & 42 \\
    \hline
    fashion-mnist      & 0.54 & 324.79                           & 1.00 & 52.91                                  & 0.94 & 60.89                                                    & 1.00 & 42 \\
    \hline
    gist                   & 1.00 & 3.55                           & 1.00 & 2.63                                     & 0.95 & 149.58                                                   & 1.00 & 42 \\
    \hline
    glove-25              & 1.00 & 78.78                          & 1.00 & 33.52                              & 1.00 & 552.67                                                  & 1.00 & 42 \\
    \hline
    glove-100             & 1.00 & 21.16                          & 1.00 & 16.52                                & 0.99 & 155.90                                                  & 1.00 & 42 \\
    \hline
    sift                  & 1.00 &  24.52                          & 1.00 & 16.40                               & 1.00 & 275.07                                                    & 1.00 & 42 \\
    \hline
    deep-image             & 0.00 & 0.00                           & 0.00 & 0.00                                 & 0.00 & 0.00                                                     & 1.00 & 42 \\
    \hline
    mnist                   & 0.00 & 0.00                          & 0.00 & 0.00                                 & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    glove-50               & 0.00 & 0.00                           & 0.00 & 0.00                              & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    lastfm                 & 0.00 & 0.00                           & 0.00 & 0.00                               & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=100$}
    \label{table:results:ann-100}
    \vskip 0.15in
    \begin{center}
    \begin{small}
    \begin{sc}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|}
    \textbf{Dataset}  & \multicolumn{2}{|c|}\textbf{faiss-ivf} & \multicolumn{2}{|c|}\textbf{bruteforce-blas} & \multicolumn{2}{|c|}\textbf{hnsw(faiss)} & \multicolumn{2}{|c|}\textbf{CAKES} \\
    &                    Recall & QPS                           & Recall & QPS                           & Recall & QPS                                           & Recall & QPS \\
    \hline
    nytimes                & 0.61 &  0.71                          & 0.99 & 10.71                              & 0.00 & 0.00                                          & 1.00 & 42 \\
    \hline
    fashion-mnist         & 1.00 & 111.47                           & 0.99 & 16.02                                  & 0.99 & 277.80                                                    & 1.00 & 42 \\ 
    \hline
    gist                   & 1.00 & 2.70                           & 0.99 & 0.80                                 & 0.99 & 59.71                                                    & 1.00 & 42 \\
    \hline
    glove-25              & -- & --                                & -- & --                                & -- & --                                                    & 1.00 & 42 \\
    \hline
    glove-100             & 0.99 &  7.52                          & 0.99 & 3.11                                  & 0.99 & 92.58                                                    & 1.00 & 42 \\
    \hline
    sift                  & 1.00 &  23.50                          & 1.00 & 6.51                                  & 0.99 & 179.14                                                    & 1.00 & 42 \\
    \hline
    deep-image             & 0.00 & 0.00                           & 0.00 & 0.00                                & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    mnist                   & 0.00 & 0.00                          & 0.00 & 0.00                                  & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    glove-50               & 0.00 & 0.00                           & 0.00 & 0.00                              & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    lastfm                 & 0.00 & 0.00                           & 0.00 & 0.00                             & 0.00 & 0.00                                                    & 1.00 & 42 \\
    \hline
    \end{tabular}
    \end{sc}
    \end{small}
    \end{center}
    \vskip -0.1in
    \end{table*}
